```{r, message = F}
library(RNASeqPower)
library(dplyr)
library(tidyverse)
library(ggplot2)
```

This calculation of sample size requires an input of:
1) sequence depth, defined as the ratio of bases sequenced to the size of the genome.
2) Biological coefficient of variation, within a group, cv = sd/mean.
3) Effect size is the biological effect one would aim to detect (commonly 1.5 or 2)(same as mean fold change).
4) Alpha, type 1 rate of error.
5) Power one would like to achieve.


```{r}
depth = 20
cv = 0.4
cv2 = 0.4
effect = c(1.25, 1.5, 1.75, 2)
alpha = 0.05
power = c(0.8, 0.9, 0.95)
```


```{r}
samplesizes <- rnapower(depth=depth, cv=cv, cv2 = cv2, effect = effect,
alpha= alpha, power=power)

samplesizes<-samplesizes%>%
  as.tibble(samplesizes)%>%
  add_column(effect)%>%
  pivot_longer(!effect, names_to="power", values_to = "samplesize")

knitr::kable(samplesizes, "pipe")
```

```{r}
ggplot(samplesizes)+
  geom_line(mapping = aes(x = effect, y =samplesize, color = power))+
  labs(title = "Sample Size Calculator from desired Power and Effect", x = "Effect (Mean Fold Change)", y = "Sample Size", color = "Desired Power")+
  theme_linedraw()
```

**Interpretation** As the observed mean fold change between groups gets larger, it takes a smaller sample size to prove a difference between two populations.















